# Which platforms to examine?

We need to figure out which platforms (outside of human, mouse and rat) would have decent amounts of data to examine. The other big possibililties are of course:

*Saccharomyces cerevisiae*
*Caenorhabditis elegans*
*Drosophila melanogaster*
*Arabidopsis Thaliana*
*Xenopus laevis*
*Plasmodium / Anopholes Gambiae*
*Danio rerio* - this might be more difficult without the data automatically in 
Bioconductor, but could still be done

All of the above except D. rerio have CDF files on Bioconductor, and really, we can get almost anything we want off of the Affymetrix(r) website.

# What datasets are available?

Look at the GEO database, and see for each organism what Affymetrix(r) platforms are available, how many experiments are there, and have raw (CEL) data to go with them.

```{r surfGeo}
require(GEOmetadb)
# getSQLiteFile() # run this once. Ran Aug 27, 2012

con <- dbConnect(SQLite(),'GEOmetadb.sqlite')

useOrgs <- c("Saccharomyces cerevisiae",
						 "Homo sapiens",
						 "Mus musculus",
						 "Rattus norvegicus",
						 "Caenorhabditis elegans",
						 "Drosophila melanogaster",
						 "Arabidopsis Thaliana",
						 "Xenopus laevis",
						 "Anopholes Gambiae",
						 "Danio rerio")


gplOrgs <- paste("SELECT gpl.title,",
									"gpl.catalog_number,",
									"gpl.data_row_count,",
									"gpl.organism,",
									"gpl.gpl,",
									"gpl.description",
									" FROM gpl WHERE ",
									"gpl.manufacturer='Affymetrix' AND ",
									"gpl.organism='", useOrgs, "'", sep="")

names(gplOrgs) <- useOrgs

gplInfo <- lapply(names(gplOrgs), function(inOrg){
	affyGPL <- dbGetQuery(con, gplOrgs[inOrg])
	write.table(affyGPL, file=paste(inOrg, ".txt", sep=""), sep="\t", row.names=F)
})

```

After looking through the results, come up with either new search strings for the sql or actual lists of GPL's to use.

```{r gplDef}
defGPL <- list(celegans=c("GPL200", "GPL13993", "GPL13995"), 
							 drerio="GPL1319",
							 dmelano=c("GPL1322", "GPL13770"),
							 scerevisiae=c("GPL90", "GPL13150"),
							 xlaevis="GPL10756")

srchGPL <- list(hsapiens=c("'%Affymetrix Human Genome U133 Plus 2.0 Array%'",
													 "'%Affymetrix GeneChip Human Genome U133 Plus 2.0 Array%'",
													 "'%Human Genome U133 Plus 2.0%'"),
								mmusculus=c("'%Affymetrix GeneChip Mouse Genome 430 2.0%'",
														"'%Affymetrix Mouse Genome 430 2.0 Array%'"),
								rnorvegicus=c("'%Affymetrix Rat Genome 230 2.0 Array%'",
															"'%Affymetrix GeneChip Rat Genome 230 2.0 Array%'"))
# for each 'srchGPL', go in and query the gpl table and see what we get back as
# far as organism, etc

gplStr <- paste("SELECT gpl.title,",
									"gpl.catalog_number,",
									"gpl.data_row_count,",
									"gpl.organism,",
									"gpl.gpl,",
									"gpl.description",
									" FROM gpl WHERE ",
								"gpl.title LIKE ", collapse="")

gplUSE <- lapply(srchGPL, function(inStr){
	tmpDat <- lapply(inStr, function(sqlQ){
		fullQ <- paste(gplStr, sqlQ, sep="")
		dbGetQuery(con, fullQ)
	})
})

defGPL2 <- lapply(gplUSE, function(x){
	aG <- unique(unlist(sapply(x, function(y){y$gpl})))
})

allGPL <- c(defGPL2, defGPL)
```

We have gotten out the **GPL** for Affymetrix(r) arrays for each model organism. Now we want to find those samples 
that have supplementary data for each one, and then get the unique *GSE's*. We will also verify that the organism in
**Ch1** matches the organism on the array.

```{r getSamples}
useTables <- c("gsm", "gse_gsm", "gse", "gse_gpl", "gpl")
tableNames <- sapply(useTables, function(x){
	tmpID <- dbListFields(con, x)
	paste(x, tmpID, sep=".")
})
tableNames <- unlist(tableNames, use.names=F)

getSql <- paste("select * FROM gsm JOIN gse_gsm ON gsm.gsm=gse_gsm.gsm",
								" JOIN gse ON gse_gsm.gse=gse.gse",
								" JOIN gse_gpl ON gse_gpl.gse=gse.gse",
								" JOIN gpl ON gse_gpl.gpl=gpl.gpl",
								" WHERE",
								" gsm.supplementary_file LIKE '%CEL.gz' AND",
								" gpl.gpl IN ", sep="")

affyData <- lapply(allGPL, function(inGPL){
	useGPL <- paste("'", inGPL, "'", sep="")
	useGPL <- paste("(", paste(useGPL, collapse=","), ")", sep="")
	q <- paste(getSql, useGPL, sep="", collapse="")
	qDat <- dbGetQuery(con, q)
	names(qDat) <- tableNames
	
	sameOrg <- qDat$gsm.organism_ch1 == qDat$gpl.organism
	qDat <- qDat[sameOrg,]
	list(nExp=length(unique(qDat$gse.gse)), sampDat=qDat)
})


```