% Affymetrix MisMatch (MM) Probes: Useful After All
% Robert M Flight, Abdallah Eteleeb, Eric C Rouchka
% 14/10/12

```{r functionDefs, include=FALSE}
tableCat <- function(inFrame){
	outText <- paste(names(inFrame), collapse=" | ")
	outText <- c(outText, paste(rep("---", ncol(inFrame)), collapse=" | "))
	invisible(apply(inFrame, 1, function(inRow){
		outText <<- c(outText, paste(inRow, collapse=" | "))
	}))
	return(outText)
}

probeClass <- function(probeIDs){
	sapply(strsplit(probeIDs, ".", fixed=T), function(y){y[1]})
}

probeSetName <- function(probeID){
	splitName <- strsplit(probeID, ".", fixed=T)[[1]]
	nSplit <- length(splitName)
	rmSplit <- -1 * c(1, nSplit-1, nSplit)
	paste(splitName[rmSplit], sep=".", collapse=".")
}

sortProbes <- function(probeIDs){
	splitIDs <- strsplit(probeIDs, ".", fixed=T)
	endIndx <- sapply(splitIDs, function(x){
		nEnt <- length(x)
		as.numeric(x[c(nEnt-1, nEnt)])
	})
	endIndx <- t(endIndx)
	order(endIndx[,1], endIndx[,2])
}
```

```{r loadPackagesData, include=FALSE}
require(ggplot2)
require(plyr)
require(VennDiagram)
require(hgu133plus2.db)
require(hgu133plus2probe)
require(org.Hs.eg.db)

load("counts_Plots_etc_allOrgs.RData")
```

# Custom CDF

CDF: Chip Definition File
- Defines how the individual probes on the array are organized into probesets
- Possible to define **custom** groupings of probes based on your own criteria


# BrainArray

- the BrainArray group has been doing this for quite a while
- x samples in **GEO** that have BrainArray CDFs